---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tvcm

The goal of this package is to provide tools to fit time-varying coefficient models. 

## Installation

```{r, eval=FALSE}
devtools::install_gitlab("inqs909/tvcm")
```


### Windows

You will need to install rtools to allow the `devtools` package to install packages from a remote repository: [https://cran.r-project.org/bin/windows/Rtools/](https://cran.r-project.org/bin/windows/Rtools/).

Make sure to update R as well.

## Functions

The main functions for this package are the `tvcm`, `binary_vcm`, and `pois_vcm` functions. They are designed to be similar with other functions that fit models. Additionally, there are functions to compute the optimal bandwidth using a cross-validation approach.


## Estimation

The estimates are obtained using either a local least-squares or local likelihood approach. The varying-coefficients are approximated using a local-linear model. 

## Standard Errors

The standard errors are obtained using a bootstrap method. Due the correlated nature of longitudinal data, bootstrap standard errors provide more accurate results. The functions will provide both the standard errors and point-wise percentiles for a value of a varying-coefficient functions.  


## Plotting

The `plot()` function will generate plots of the time-varying coefficient model.